---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# HindiMorph

Morphological analysis of Hindi. This package gives the class of a word of Hindi, using `RDRPOSTagger` (http://rdrpostagger.sourceforge.net/)

**Sorry, This package works on UNIX OS (Linux or MacOS) only.**

## Installation

### Requirements
You need to install pyenv and python2.7.13 to use HindiMorph.

```
git clone git://github.com/yyuu/pyenv.git ~/.pyenv
echo 'export PYENV_ROOT="$HOME/.pyenv"' >> ~/.bash_profile # or .bashrc
echo 'export PATH="$PYENV_ROOT/bin:$PATH"' >> ~/.bash_profile
echo 'eval "$(pyenv init -)"' >> ~/.bash_profile

pyenv install 2.7.13
```

### HindiMorph
You can install HindiMorph from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ymattu/HindiMorph")
```

## Example
This package contains only one function `hindi_morph`. This function accepts only dataframe and you just specify the column name of the text. Then a dataframe contains word, class, and documentid is returned.

```{r example}
library(HindiMorph)

# sample data
df <- data.frame(txt = c("कि जब तक ये सब बातें न हो लेंगी","तब तक यह पीढ़ी जाती न रहेगी।[31]आकाश और पृथ्वी टल जाएंगे","परन्तु मेरी बातें कभी न टलेंगी।"))

res <- hindi_morph(df, txt)
res
```
